Conditions for $d$-local-connectedness of boundaries of hyperbolic groups

### 2020-01-21 paper.tex
Altered the ddag and Sd symbols.

\begin{proposition}
  Suppose that $G$ satisfies $\ddag'_M$ for $M = D+2$. Then there exists $k$
  such that for $n$ sufficiently large there is a map
  $i^n_{n+1}\from \Skel_1 K_n \to \Skel_1 K_{n+1}$ satisfying the following
  conditions:
  \begin{enumerate}
    \item for each $n$, $i^n_{n+1}$ is an affine map on the subdivision
      $\sd_k\Skel_1 K_n$,
    \item for any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq ?$, and
    \item for each $n$, $i^n_{n+1}$ is affine homotopic to a map that factors
      through $p^\infty_{n+1}\from \boundary G \to K_{n+1}$.
  \end{enumerate}
\end{proposition}

@@

@@

\begin{definition}
  We say that $G$ satisfies $\Sd_M$ if there exists $k$ such that for any $n$
  sufficiently large and any affine map $f\from \boundary\Delta^2$ \todo{Do
  this}
\end{definition}

@@

\begin{restatable}{theorem}{ddagimpliesLCd}\label{thm:ddagimpliesLCd}
  If $G$ satisfies $\Sd_M$ for all $M$ then $\boundary G$ is locally simply
  connected.
\end{restatable}

@@

\begin{proposition}\label{prop:ddag_implies_i}
  Let $d \geq -1$. Suppose that $G$ satisfies the conditions $\Sd{d-1}$ and
  $\dd{d}$. Then there are constants $n_0$, $k$ and $\epsilon$ such that for
  each $n\geq n_0$ there is map $i^n_{n+1}\from\Skel_{d+1} K_n \to \Skel_{d+1}
  K_{n+1}$ such that the following conditions hold.
  \begin{enumerate}
    \item For any $x \in \Vertices(K_n)$, $\dist(x, i_{n+1}^n(x)) \leq
      \epsilon$.
    \item The map $i^n_{n+1}$ is affine on the subdivision $\sd^k\Skel_{d+1}
      K_n$ of $\Skel_{d+1}K_n$.
    \item The map $i^n_{n+1}\restricted{\Skel_d K_n}$ admits a factoring.
  \end{enumerate}
\end{proposition}

\begin{proof}
  The condition $\dd{-1}$ implies the infinitude of $G$, so
  \cref{lem:near_geod_rays} is applicable. For $x \in \Vertices{K_n}$ choose an
  infinite geodesic ray $\alpha_x$ such that $\alpha(0) = 1$ and
  $\dist(\alpha(n), x) \leq 4\delta$. Define $i^n_{n+1}(x) =
  \alpha_x(n+1)$. Then $i^n_{n+1}$ satisfies the first requirement with
  $\epsilon = 4\delta+2$ and satisfies the second requirement automatically.

@@

Throughout the remainder of this section we assume that $G$ satisfies $\dd{d-1}$ 
and $\Sd{d}$. Let $n_0$, $k$ and $\epsilon$ be the constants given in 
\cref{prop:ddag_implies_i}, and for $n\geq n_0$ let $i^n_{n+1} 
\from \sd^k\Skel_{d+1} K_n \to \Skel_{d+1} K_{n+1}$ be the affine map given by 
that proposition.  For $n \geq m \geq n_0$ let $i^m_n$ be the composition 
$i^{n-1}_n \composed \dotsb \composed i^m_{m+1} \from \Skel_{d+1} K_m \to 
\Skel_{d+1} K_n$.  This map is affine on a degree $k^{n-m}$ subdivision of 
$\Skel_{d+1} K_m$.

>>>>

\begin{proposition}
  Suppose that $G$ satisfies $\ddag'_M$ for $M = D+2$. Then there exists $k$
  such that for $n$ sufficiently large there is a map
  $i^n_{n+1}\from \Skel_1 K_n \to \Skel_1 K_{n+1}$ satisfying the following
  conditions:
  \begin{enumerate}
    \item for each $n$, $i^n_{n+1}$ is an affine map on the subdivision
      $\sd_k\Skel_1 K_n$,
    \item for any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq ?$, and
    \item for each $n$, the map $i^n_{n+1}$ is affine homotopic to a map that
      factors through $p^\infty_{n+1}\from \boundary G \to K_{n+1}$.
  \end{enumerate}
\end{proposition}

@@

\todo{Proposition below}

\begin{proposition}\label{prop:extendingaffinemaps2}
  Something about extending affine maps.
\end{proposition}

@@

\begin{definition}
  We say that $G$ satisfies $\S_M$ if there exists $k$ such that for any $n$
  sufficiently large and any affine map $f\from \boundary\Delta^2$ \todo{Do
  this}
\end{definition}

@@

\begin{restatable}{theorem}{ddagimpliesLCd}\label{thm:ddagimpliesLCd}
  If $G$ satisfies $\S_M$ for all $M$ then $\boundary G$ is locally simply
  connected.
\end{restatable}

@@

\begin{proposition}\label{prop:ddag_implies_i}
  Let $d \geq -1$. Suppose that $G$ satisfies the conditions $\S^{d-1}$ and
  $\ddag^{d}$. Then there are constants $n_0$, $k$ and $\epsilon$ such that for
  each $n\geq n_0$ there is map $i^n_{n+1}\from\Skel_{d+1} K_n \to \Skel_{d+1}
  K_{n+1}$ such that the following conditions hold.
  \begin{enumerate}
    \item For any $x \in \Vertices(K_n)$, $\dist(x, i_{n+1}^n(x)) \leq
      \epsilon$.
    \item The map $i^n_{n+1}$ is affine on the subdivision $\sd^k\Skel_{d+1}
      K_n$ of $\Skel_{d+1}K_n$.
    \item The map $i^n_{n+1}\restricted{\Skel_d K_n}$ admits a factoring.
  \end{enumerate}
\end{proposition}

\begin{proof}
  The condition $\ddag^{-1}$ implies the infinitude of $G$, so
  \cref{lem:near_geod_rays} is applicable. For $x \in \Vertices{K_n}$ choose an
  infinite geodesic ray $\alpha_x$ such that $\alpha(0) = 1$ and
  $\dist(\alpha(n), x) \leq 4\delta$. Define $i^n_{n+1}(x) =
  \alpha_x(n+1)$. Then $i^n_{n+1}$ satisfies the first requirement with
  $\epsilon = 4\delta+2$ and satisfies the second requirement automatically.

@@

Throughout the remainder of this section we assume that $G$ satisfies $\ddag^{d-1}$ 
and $\S^{d}$. Let $n_0$, $k$ and $\epsilon$ be the constants given in 
\cref{prop:ddag_implies_i}, and for $n\geq n_0$ let $i^n_{n+1} 
\from \sd^k\Skel_{d+1} K_n \to \Skel_{d+1} K_{n+1}$ be the affine map given by 
that proposition.  For $n \geq m \geq n_0$ let $i^m_n$ be the composition 
$i^{n-1}_n \composed \dotsb \composed i^m_{m+1} \from \Skel_{d+1} K_m \to 
\Skel_{d+1} K_n$.  This map is affine on a degree $k^{n-m}$ subdivision of 
$\Skel_{d+1} K_m$.
